### 2014-11-12 implementation.tex
Remove fig 4.

In the paper~\cite{cruz-ppdp14}, the LM virtual machine was measured and
compared against implementations of similar programs but written in other
languages. For instance, the LBP program was found to be around 2 times slower
than GraphLab, while N Queens program was found to be around 10 to 15 slower
than a sequential C implementation. Some of those programs were compared against
a Python implementations and LM faired fairly well. In this section, we measure
the impact of the coordination mechanisms we have implemented for the CLM
virtual machine.

Fig.~\ref{results:comparison1} shows the comparison between the original virtual
machine and the new virtual machine with coordination mechanisms. All the
programs benchmarked do not use any kind of coordination. As hoped for, there
is no degradation of performance by adding coordination mechanisms. Since we also
performed general performance improvements, programs such as PageRank and Greedy
Graph Coloring programs now perform better than before.

\begin{topfig}
   \begin{center}
      \subfloat[]{\includegraphics[width=8cm]{results/comparison1.png}}
   \end{center}
   \scap{results:comparison1}{Measuring the overhead of coordination mechanisms. The \textbf{Old}
   bars represent the performance of the original virtual machine, while
   \textbf{New} is the relative performance of the new version that includes
   coordination mechanisms.}
\end{topfig}

>>>>

In the paper~\cite{cruz-ppdp14}, the LM virtual machine was measured and
compared against implementations of similar programs but written in other
languages. For instance, the LBP program was found to be around 2 times slower
than GraphLab, while N Queens program was found to be around 10 to 15 slower
than a sequential C implementation. Some of those programs were compared against
a Python implementations and LM faired fairly well. We measured
the impact of the coordination mechanisms implemented for the CLM
virtual machine on regular LM programs and saw very little to no degration.
Since we also performed general performance improvements, programs such as
PageRank and Greedy Graph Coloring programs now perform better than before.
